E-jection fraction - Tracking how your website pumps out E-Mails

### 2016-05-05 introduction.tex
added intro, pb bg, needs formatting

\chapter{Introduction}
\paragraph{}
	The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the Web has made it possible for the general public to access it anywhere and on multiple devices like phones, laptops, personal digital assistants, and even on TVs and cars. This has ushered in an era of responsive web applications which depend on user input. While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost. Attackers have an added incentive to break into user's e-mail accounts more than ever. E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions. Thus, the impact an attacker can have by having control over the e-mail communication sent by websites to users is of an enormous magnitude.

@@

\paragraph{Structure of document} % describes the remaining sections and gives a short desc about them
This thesis document is divided logically into the following sections:
\begin{itemize}
	\item Chapter 2 discusses the background of E-Mail Header Injection, a brief history of the vulnerability, and enumerates the languages and platforms affected by this vulnerability.

@@

\paragraph{} % summary paragraph
We hope that our research sheds some light on this relatively less well-known vulnerability, and find out its prevalence on the World Wide Web. In summary, we make the following contributions:
\begin{itemize}

@@

\paragraph{}

>>>>

	The World Wide Web has single-handedly brought about a change in the way we use computers. The ubiquitous nature of the Web has made it possible for the general public to access it anywhere and on multiple devices like phones, laptops, personal digital assistants, and even on TVs and cars. This has ushered in an era of responsive web applications which depend on user input. While this rapid pace of development has improved the speed of dissemination of information, it does come at a cost. Attackers have an added incentive to break into user's e-mail accounts more than ever. E-Mail accounts are usually connected to almost all other online accounts of a user, and e-mails continue to serve as the principal mode of official communication on the web for most institutions. Thus, the impact an attacker can have by having control over the e-mail communication sent by websites to users is of an enormous magnitude.

@@

\subsection*{Structure of document} % describes the remaining sections and gives a short desc about them
This thesis document is divided logically into the following sections:
\begin{itemize}
	\item Chapter 2 discusses the background of E-Mail Header Injection, a brief history of the vulnerability, and enumerates the languages and platforms affected by this vulnerability.

@@

We hope that our research sheds some light on this relatively less well-known vulnerability, and find out its prevalence on the World Wide Web. In summary, we make the following contributions:
\begin{itemize}

@@

### 2016-05-05 paper.tex
added intro, pb bg, needs formatting

@@

\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{17,686,161}

\newcommand{\forms}{5,562,533}
\newcommand{\formsDelta}{31.45\%}

\newcommand{\emailforms}{918,988}
\newcommand{\emailformsDelta}{16.52\%}

\newcommand{\fuzzed}{756,588}
\newcommand{\fuzzedDelta}{82.33\%}

\newcommand{\recd}{44,735}
\newcommand{\recdDelta}{5.91\%}

\newcommand{\malfuzzed}{38,989}
\newcommand{\malfuzzedDelta}{87.16\%}

\newcommand{\success}{433}
\newcommand{\successDelta}{1.11\%}

\newcommand{\domains}{182}

% these refer to unique domains, not unique forms
\newcommand{\uniqueforms}{650,394}
\newcommand{\uniqueemailforms}{151,795}

@@

	\section{Introduction}
	The \textit{proceedings} are the records of a conference.
	ACM seeks to give these conference by-products a uniform,
	high-quality appearance.  To do this, ACM has some rigid
	requirements for the format of the proceedings documents: there
	is a specified format (balanced  double columns), a specified
	set of fonts (Arial or Helvetica and Times Roman) in
	certain specified sizes (for instance, 9 point for body copy),
	a specified live area (18 $\times$ 23.5 cm [7" $\times$ 9.25"]) centered on
	the page, specified size of margins (1.9 cm [0.75"]) top, (2.54 cm [1"]) bottom
	and (1.9 cm [.75"]) left and right; specified column width
	(8.45 cm [3.33"]) and gutter size (.83 cm [.33"]).

	The good news is, with only a handful of manual
	settings\footnote{Two of these, the {\texttt{\char'134 numberofauthors}}
		and {\texttt{\char'134 alignauthor}} commands, you have
		already used; another, {\texttt{\char'134 balancecolumns}}, will
		be used in your very last run of \LaTeX\ to ensure
		balanced column heights on the last page.}, the \LaTeX\ document
	class file handles all of this for you.

	The remainder of this document is concerned with showing, in
	the context of an ``actual'' document, the \LaTeX\ commands
	specifically available for denoting the structure of a
	proceedings paper, rather than with giving rigorous descriptions
	or explanations of such commands.

>>>>

% for title caps
\usepackage{titlecaps}
\Addlcwords{and, the, or, of, that, our, by, a, prevent, for}

@@

\newcommand{\dq}[1]{``{#1}''}
%% THIS IS THE DATA FOR OUR THESIS, UPDATING HERE WILL UPDATE EVERYWHERE %%
\newcommand{\urls}{21,675,680}

\newcommand{\forms}{6,794,917}
\newcommand{\formsDelta}{31.35\%}

\newcommand{\emailforms}{1,132,157}
\newcommand{\emailformsDelta}{16.66\%}

\newcommand{\fuzzed}{934,016}
\newcommand{\fuzzedDelta}{82.50\%}

\newcommand{\recd}{52,724}
\newcommand{\recdDelta}{5.64\%}

\newcommand{\malfuzzed}{46,156}
\newcommand{\malfuzzedDelta}{87.54\%}

\newcommand{\success}{496}
\newcommand{\successDelta}{1.07\%}

\newcommand{\domains}{222}
\newcommand{\ips}{292}
% these refer to unique domains, not unique forms
\newcommand{\uniqueforms}{1,019,921}
\newcommand{\uniqueemailforms}{197,570}

@@

	\section{Introduction}
	\input{introduction}

	\input{problem_background}
